---
title: "Odds Ratio Case Studies"
output: html_notebook
---

```{r, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
library(tidyverse)
library(lubridate)
library(sp)
library(sf)
library(raster)
library(rgeos)
library(rgdal)
library(viridis)
library(gridExtra)
library(rasterVis)
require(spatialEco)
library(plotly)
library(classInt)

set.seed(1)

# Retrieved with thanks from http://strimas.com/spatial/hexagonal-grids/
make_grid <- function(x, cell_diameter, cell_area, clip = FALSE) {
  if (missing(cell_diameter)) {
    if (missing(cell_area)) {
      stop("Must provide cell_diameter or cell_area")
    } else {
      cell_diameter <- sqrt(2 * cell_area / sqrt(3))
    }
  }
  ext <- as(extent(x) + cell_diameter, "SpatialPolygons")
  projection(ext) <- projection(x)
  # generate array of hexagon centers
  g <- spsample(ext, type = "hexagonal", cellsize = cell_diameter, 
                offset = c(0.5, 0.5))
  # convert center points to hexagons
  g <- HexPoints2SpatialPolygons(g, dx = cell_diameter)
  # clip to boundary of study area,.
  if (clip) {
    g <- gIntersection(g, x, byid = TRUE)
  } else {
    g <- g[x, ]
  }
  # clean up feature IDs
  row.names(g) <- as.character(1:length(g))
  return(g)
}
    
# read in files
tweets <- invisible(read_csv("emoji_trunc.csv"))
tweets <- tweets %>%
  mutate(date = as_datetime(created_at/1000, tz = "Asia/Singapore")) %>%
  mutate(weekday = wday(date))
insta <- invisible(read_csv("instagram_trunc.csv"))
insta <- insta %>%
  mutate(date = as_datetime(created_at)) %>%
  mutate(weekday = wday(date))
shape <- invisible(readOGR(dsn = 'sg-shape', layer ='sg-all'))
shape <- gBuffer(shape, byid=TRUE, width=0) # clean up polygons
```

**Case 1: Sentiments on Weekdays vs Weekends**
```{r, message = FALSE, warning = FALSE, error = FALSE}
t_wday <- tweets %>%
  filter(weekday < 6) # filter only tweets made on weekdays
  
t_wend <- tweets %>%
  filter(weekday > 5) # filter only tweets made on weekends  
  
i_wday <- insta %>%
  filter(weekday < 6) # filter only igs made on weekdays
  
i_wend <- insta %>%
  filter(weekday > 5) # filter only igs made on weekends  
```
  
**Case 2: Different periods of the day**
```{r, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}

# Remove NAs
tweets <- drop_na(tweets)
tweets.sf <- st_as_sf(tweets, coords = c('lon','lat'), crs=4326)

insta <- drop_na(insta)
insta.sf <- st_as_sf(insta, coords=c('lon', 'lat'), crs=4326)
insta.sf <- insta.sf %>% 
  select(created_at, pos, neu, neg, date, weekday, geometry) %>%
  mutate(sent = pos-neu)

# Create hex grid
shape_utm <- spTransform(shape, CRS(proj4string(shape)))
hex_grid <- make_grid(shape_utm, cell_area = 0.0001, clip = T)
hex.sf <- st_as_sf(hex_grid, crs=4326)
hex.sf <- tibble::rowid_to_column(hex.sf, "hexID")

# Change column names
colnames(tweets.sf) <- c("t.neg", "t.neu", "t.pos", "t.created_at", "t.sent", "datetime", "wday", "geometry")
colnames(insta.sf) <- c("i.created_at", "i.pos", "i.neu", "i.neg", "datetime", "wday", "sent", "geometry")

# Add time periods
periods = c("12am - 6am", "6am - 12pm", "12pm - 6pm", "6pm - 12am")

tweets.periods <- tweets.sf %>% 
  mutate(period = case_when(
    hour(datetime) < 6 ~ "12am - 6am", 
    hour(datetime) >= 6 & hour(datetime) < 12 ~ "6am - 12pm",
    hour(datetime) >= 12 & hour(datetime) < 18 ~ "12pm - 6pm",
    hour(datetime) >= 18 ~ "6pm - 12am"
  ))

insta.periods <- insta.sf %>% 
  mutate(period = case_when(
    hour(datetime) < 6 ~ "12am - 6am", 
    hour(datetime) >= 6 & hour(datetime) < 12 ~ "6am - 12pm",
    hour(datetime) >= 12 & hour(datetime) < 18 ~ "12pm - 6pm",
    hour(datetime) >= 18 ~ "6pm - 12am"
))

# Points in polygon
t.join <- st_join(tweets.periods, hex.sf, join = st_within)
t.join.df <- as.data.frame(t.join)
t.join.df <- drop_na(t.join.df)
t.join.summary <- t.join.df %>% group_by(hexID, period) %>% summarise(t.count = n(), t.pos = sum(t.pos), t.neg = sum(t.neg), t.neu = sum(t.neu)) 
t.join.summary <- as.data.frame(t.join.summary)

i.join <- st_join(insta.periods, hex.sf, join = st_within)
i.join.df <- as.data.frame(i.join)
i.join.df <- drop_na(i.join.df )
i.join.summary <- i.join.df %>% group_by(hexID, period) %>% summarise(i.count = n(), i.pos = sum(i.pos), i.neg = sum(i.neg), i.neu = sum(i.neu)) 
i.join.summary <- as.data.frame(i.join.summary)

# Add default values for missing hexagons
for (i in hex.sf$hexID) {
  if (!(i %in% i.join.summary$hexID)) {
    for (time in periods) {
      i.join.summary <- rbind(i.join.summary, data.frame(i.count=1, i.pos=0, i.neg=0, i.neu=0, hexID=i, period = time))
    }
  }
  if (i %in% i.join.summary$hexID) {
    temp <- i.join.summary %>% filter(hexID == i)
    for (time in periods) {
      if (!(time %in% temp$period)) {
        i.join.summary <- rbind(i.join.summary, data.frame(i.count=1, i.pos=0, i.neg=0, i.neu=0, hexID=i, period = time))
      }
    }
  }
  
  if (!(i %in% t.join.summary$hexID)) {
    for (time in periods) {
      t.join.summary <- rbind(t.join.summary, data.frame(t.count=1, t.pos=0, t.neg=0, t.neu=0, hexID=i, period = time))
    }
  }
  
  if (i %in% t.join.summary$hexID) {
    temp <- t.join.summary %>% filter(hexID == i)
    for (time in periods) {
      if (!(time %in% temp$period)) {
        t.join.summary <- rbind(t.join.summary, data.frame(t.count=1, t.pos=0, t.neg=0, t.neu=0, hexID=i, period = time))
      }
    }
  }
}

# join twitter and instagram data together
#join.summary <- merge(t.join.summary, i.join.summary, by="hexID")

# Add normalized sent
t.join.summary <- t.join.summary %>% mutate(t.norm = (t.pos-t.neg)/t.count)
i.join.summary <- i.join.summary %>% mutate(i.norm = (i.pos-i.neg)/i.count)

# add geometry back
t.summary.sf <- merge(x = t.join.summary, y = hex.sf, by = "hexID")
i.summary.sf <- merge(x = i.join.summary, y = hex.sf, by = "hexID")

temp <- t.summary.sf %>% filter(period == "12pm - 6pm")

save(t.summary.sf, file="tweets.periods")
save(i.summary.sf, file="insta.periods")

# Plot the hex maps
class_int <- classIntervals(t.summary.sf$t.norm, n = 5, style = "jenks")
rounded <- round(class_int$brks,3)

p <- ggplot() +
  geom_sf(data = t.summary.sf, aes(fill=cut(t.norm, class_int$brks), geometry=geometry, text=paste0("Sentiment: ", t.norm)), lwd=0) +
  theme_void() +
  coord_sf() +
  scale_fill_viridis(
    name="Normalized Sentiment",
    discrete=T,
    labels = rounded,
    guide=guide_legend(
      keyheight = unit(2, units = "mm"),
      keywidth=unit(12, units = "mm"),
      label.position = "bottom",
      title.position = 'top',
      nrow=1)) +
  labs(
    title = "Twitter Sentiment in Singapore",
    subtitle = "Normalized Sentiment score = (Positive - Negative)/Total Count",
    caption = "Data: Ate Poorthuis | Creation: Dragon Minions"
  ) +
  theme(
    text = element_text(color = "#22211d"),
    plot.background = element_rect(fill = "#ffffff", color = NA),
    panel.background = element_rect(fill = "#ffffff", color = NA),
    legend.background = element_rect(fill = "#ffffff", color = NA),
    plot.title = element_text(size= 18, hjust=0.01, color = "#4e4d47", margin = margin(b = -0.1, t = 0.4, l = 2, unit = "cm")),
    legend.position = c(0.82, 0.09),
    panel.grid.major = element_line(colour = 'transparent'),
    panel.grid.minor = element_line(colour = 'transparent')
  ) +
  facet_grid(. ~ period)

p
```
  
  


``` {r}
join.summary <- merge(t.join.summary, i.join.summary, by="hexID")
#join.summary <- join.summary %>% select('t.count', 't.pos', 't.neg', 't.neu', 'i.count', 'i.pos', 'i.neg', 'i.neu', 'hexID') %>% drop_na()

kml.data <- merge(join.summary, hex.sf, by = "hexID") %>% st_as_sf()
kml.data <- st_as_sf(kml.data)
kml.data <- kml.data %>% mutate(t.norm = (t.pos-t.neg)/t.count, i.norm = (i.pos-i.neg)/i.count, odds=t.pos/i.pos)
kml.data[!is.finite(kml.data$odds),]$odds <- 0
# ggplot(kml.data) + geom_histogram(aes(x=odds), bins=30)

# Plot a histogram of the odds
p <- ggplot() +
  geom_sf(data = kml.data, aes(fill=odds, geometry=geometry, text=paste0("Odds Ratio: ", odds)), lwd=0) + 
  theme_void() +
  coord_sf() +
  # scale_fill_viridis(
  #   breaks=c(0,0.25,0.3,0.35,0.4,0.45),
  #   name="Normalized Sentiment",
  #   guide=guide_legend(
  #     keyheight = unit(3, units = "mm"),
  #     keywidth=unit(12, units = "mm"),
  #     label.position = "bottom",
  #     title.position = 'top',
  #     nrow=1)) +
  scale_fill_distiller(
    palette="Spectral",
    limits=c(0,2),
    breaks=c(0,0.3,0.6,1,1.5,2),
    na.value="grey",
    name="Normalized Sentiment",
    guide=guide_legend(
      keyheight = unit(3, units = "mm"),
      keywidth=unit(12, units = "mm"),
      label.position = "bottom",
      title.position = 'top',
      nrow=1)) +
  labs(
    title = "Sentiment Odds Ratio on Weekends",
    subtitle = "Normalized Sentiment score = (Positive - Negative)/Total Count",
    caption = "Data: Ate Poorthuis | Creation: Dragon Minions"
  ) +
  theme(
    text = element_text(color = "#22211d"), 
    plot.background = element_rect(fill = "#f5f5f2", color = NA), 
    panel.background = element_rect(fill = "#f5f5f2", color = NA), 
    legend.background = element_rect(fill = "#f5f5f2", color = NA),
    plot.title = element_text(size= 22, hjust=0.01, color = "#4e4d47", margin = margin(b = -0.1, t = 0.4, l = 2, unit = "cm")),
    plot.subtitle = element_text(size= 17, hjust=0.01, color = "#4e4d47", margin = margin(b = -0.1, t = 0.43, l = 2, unit = "cm")),
    plot.caption = element_text( size=12, color = "#4e4d47", margin = margin(b = 0.3, r=-99, unit = "cm") ),
    legend.position = c(0.7, 0.09),
    panel.grid.major = element_line(colour = 'transparent'), 
    panel.grid.minor = element_line(colour = 'transparent')
  )

#p
ggplotly(p, tooltip = "text") %>%
  highlight(
    "plotly_hover",
    opacityDim = 1
  )

```

We can observe that Singaporeans are marginally happier on weekends compared to weekdays. Generally, social media sentiments are more negative in industrial areas compared to residential areas, and do not change much regardless of the day. We can also notice a change from sad to happy in recreational areas such as East Coast Park and Orchard Road.

  
**Case 2: Sentiments across various Time Periods** 

We will be dividing the data into 4 time periods: 

* SGT 00:00 - 05:59 
* SGT 06:00 - 11:59  
* SGT 12:00 - 17:59 
* SGT 18:00 - 23:59

**Some general observations that we can make based on time periods:**

*Singaporeans are happiest on social media from 12:00 - 17:59.
*From 18:00 - 23:59, residential areas remain largely happy, whereas the industrial areas (South and West parts of Singapore) are least happy (probably due to the need to work overtime).
*From 00:00 - 05:59, sentiments are largely unhappy, with small ???happy??? clusters around Choa Chu Kang, Ang Mo Kio, Geylang, Bedok and Tampines areas (possibly areas with 24/7 food options, and other night activities).
*The east remains happy regardless of time period, I wonder why.
